Architectures and Open pNets

### 2018-11-30 2018-Arch-pNets/arch-pNets.tex
mise en forme verbatim OTs

\begin{example}\emph{An open-transition.}
  \label{OT:enable-composed}
  \todoEM{remplacer cette OT par une du Timer, qui aurait tous les elements presents...}
  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
  and 2 holes. One of its possible open-transition is\footnote{Note the underlined action notation that we use to represent synchronised actions, i.e. actions that are the result of a synchronisation and that we declare as \emph{non-observable}. Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector. This allows us to define a weak bisimilarity equivalence with p=compositional properties.}: 
\noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}

 \smallskip
 $  OT_2  = \openrule{ 
							(P\mapsto \delta(x4), Q\mapsto accept(x4))               
%                            \xrightarrow{\delta(x4)}_P ~~
%                            \xrightarrow{accept(x4)}_Q 
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {A1_0 \OTarrow{\underline{\delta(x4)}} A1_1}
  $
\end{example}

@@

>>>>

\begin{example}\emph{An open-transition.}
  \label{OT:enable-composed}
  \todoEM{Commenter...}
  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
  and 2 holes. Two of its possible open-transitions are:

%%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e. actions that are the result of a synchronisation and that we declare as \emph{non-observable}. Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector. This allows us to define a weak bisimilarity equivalence with p=compositional properties.}
%%   : 
%% \noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}

 \smallskip
$  OT_1  = \openrule
{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
$
\medskip

  $  OT_3  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
    \{z:=z1\} }
  {\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{12}}
  $

\end{example}

@@

\subsection{Full results of the use-case}
\label{secn:full-results}

\subsubsection{Output of the open-automaton construction}
The standard pretty-print of OTs by the tool include the transitions
of the pLTSs (controllers). This is not a full ``proof-carrying
code'', but it allows for a better understanding of the construction
of each OT.

We first show the pNet input, then the twelve generated OTs in their
verbatim form.

\small\begin{verbatim}
FailureTimerArchi
--------------------
SV0 SVs: <tick(z, t, z1), fail(zone, b1), fail(b0), _>-->alpha0,
                          [((b1->b0)/\(z1=z/\(((b1?(zone)TopInt)))+t)))]
SV1 SVs: <cancel(b1), resume(b2), resume, _>-->alpha1, (b1=b2)
SV2 SVs: <timeout, timeout, _, ask>-->alpha2
SV3 SVs: <_, reset, _, reset>-->alpha3
SV4 SVs: <init, init, _, _>-->alpha4
pLTS: Timer
- Transition: t0---init-->t1, { t := 0 z := TopInt}
- Transition: t1---tick(z, t, z1)-->t1, [(t<GET_MAX z)], { t := (t+1) z := z1}
- Transition: t1---cancel(false)-->t1, {}
- Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
- Transition: t1---timeout-->t1, [t in z], { t := (t+1)}
- Variable: t, State: t1, Value(s) = 0,0,(t+1),
- Variable: z, State: t1, Value(s) = TopInt,z1,
pLTS: Failure
- Transition: s0---init-->s1, { zone := minZone,maxZone}
- Transition: s1---timeout-->s1, {}
- Transition: s1---resume(false)-->s1, {}
- Transition: s1---fail(zone, false)-->s1, {}
- Transition: s1---fail(zone, true)-->s2, {}
- Transition: s2---fail(zone, false)-->s2, {}
- Transition: s2---resume(false)-->s2, {}
- Transition: s2---resume(true)-->s1, {}
- Transition: s2---timeout-->s3, {}
- Transition: s3---fail(zone, false)-->s3, {}
- Transition: s3---resume(false)-->s3, {}
- Transition: s3---reset-->s1, {}
- Variable: zone, State: s1, Value(s) = minZone,maxZone,
Holes: B
Holes: E

-------------------------------------------
INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 OTs
INFO  BIPArchFailureTimerMax_LTF3 -
        {t0---init-->t1, s0---init-->s1},   {},   
        [((init=:ra:117:1))/\((:ra:117:1=init))/\((init=:ra:118:1))/\((:ra:118:1=init))
          /\((alpha4=:ra:1:5))],   {t := 0, z := TopInt, zone := minZone,maxZone}
    OT1 ------------------------------------------------------------
        <t0_s0>-----:ra:1:5----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
     {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B:13:1-->},   
     [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
       /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
       /\((fail(zone, false)=:ra:12:1))
       /\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\
       ((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\
       (z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
       /\((alpha0=:ra:1:1))],
   {t := (t+1), z := z1}
    OT2 ------------------------------------------------------------
        <t1_s1>-----:ra:1:1----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B:13:1-->},
   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
     /\((fail(zone, true)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
    OT3 ------------------------------------------------------------
        <t1_s1>-----:ra:1:1----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B:17:3-->},
   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
    OT4 ------------------------------------------------------------
        <t1_s1>-----:ra:1:2----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
{t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E:112:6-->},
[(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
/\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))], {t := (t+1)}
    OT5 ------------------------------------------------------------
        <t1_s1>-----:ra:1:3----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B:13:1-->},
   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
     /\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
    OT6 ------------------------------------------------------------
        <t1_s2>-----:ra:1:1----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B:17:3-->},
   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
    OT7 ------------------------------------------------------------
        <t1_s2>-----:ra:1:2----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B:17:3-->},
   [((cancel(true)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
     /\((resume(true)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],
   {t := 0, z := TopInt}
    OT8 ------------------------------------------------------------
        <t1_s2>-----:ra:1:2----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E:112:6-->},
   [(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
     /\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))],
   {t := (t+1)}
    OT9 ------------------------------------------------------------
        <t1_s2>-----:ra:1:3----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B:13:1-->},
   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
     /\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
    OT10 ------------------------------------------------------------
        <t1_s3>-----:ra:1:1----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
   {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B:17:3-->},
   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
    OT11 ------------------------------------------------------------
        <t1_s3>-----:ra:1:2----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
   {s3---reset-->s1},   {---:hb_E:116:8-->},
   [((reset=:ra:114:1))/\((:ra:114:1=reset))/\((:hb_E:116:8=reset))/\((alpha3=:ra:1:4))],   {}
    OT12 ------------------------------------------------------------
        <t1_s3>-----:ra:1:4----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 SATISFIABLE OTs
INFO  BIPArchFailureTimerMax_LTF3 -        235 UNSATISFIABLE OTs
INFO  BIPArchFailureTimerMax_LTF3 - Total Time: 1293 ms
\end{verbatim}

OTs simplifiees a la main:

$  OT_1  = \openrule
{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
$
\medskip

$  OT_2  = \openrule
{\{B\mapsto fail(b0)\},\\
  t<GetMax(z) \land b1=false \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
  \{z:=z1\} }
{\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{11}}
$
\medskip

  $  OT_3  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
    \{z:=z1\} }
  {\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{12}}
  $
  \medskip

  $  OT_4  = \openrule
  {\{B\mapsto resume\},
    b1=false \land b2=false \land b1=b2
    \{\}  }
  {\ostate{11} \OTarrow{\underline{\alpha_1}} \ostate{11}}
  $
  \medskip

  $  OT_5  = \openrule
  {\{E\mapsto ask\},
    t \in z,
    \{t:=t+1\}  }
  {\ostate{11} \OTarrow{\underline{\alpha_2}} \ostate{11}}
  $
  \medskip

  $  OT_7  = \openrule
  {\{B\mapsto resume\},
    b1=false \land b2=false \land b1=b2,
    \{\} }
  {\ostate{12} \OTarrow{\underline{\alpha_1}} \ostate{12}}
  $
  \medskip

  $  OT_8  = \openrule
  {\{B\mapsto resume\},
    b1=true \land b2=true \land b1=b2, 
    \{t:=0, z:=TopInt\} }
  {\ostate{12} \OTarrow{\underline{\alpha_1}} \ostate{11}}
  $
  \medskip

  $  OT_9  = \openrule
  {\{E\mapsto ask\},
    t \in z,
    \{t:=t+1\} }
  {\ostate{12} \OTarrow{\underline{\alpha_2}} \ostate{13}}
  $
  \medskip

  $  OT_{10}  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),
    \{t:=t+1, z:=z1\} }
  {\ostate{13} \OTarrow{\underline{\alpha_0}} \ostate{13}}
  $
  \medskip

  $  OT_{11}  = \openrule
  {\{B\mapsto resume\},
    b1=false \land b2=false \land b1=b2,
    \{\} }
  {\ostate{13} \OTarrow{\underline{\alpha_1}} \ostate{13}}
  $
  \medskip

  $  OT_{12}  = \openrule
  {\{E\mapsto reset\},
    true,
    \{\} }
  {\ostate{13} \OTarrow{\underline{\alpha_3}} \ostate{11}}
  $
